\documentclass{article}
\usepackage[utf8]{inputenc} %File encoding

\newcommand{\gls}[1]{#1}
\newcommand{\citez}[1]{#1\protect\nocite{#1}}

% \renewenvironment{glossary}%
% {\begin{description}\setlength{\labelwidth}{35pt}%
% \setlength{\leftmargin}{\labelwidth+\labelsep}}%
% {\end{description}}%

\renewenvironment{glossary}
   {\begin{list}{}{\setlength\labelsep{\linewidth}%
                   \setlength\labelwidth{0pt}%
                   \setlength\itemindent{-\leftmargin}%
                   \let\makelabel\descriptionlabel}}
   {\end{list}}

\newenvironment{listofacronyms}
   {\begin{list}{}{\setlength\labelwidth{0pt}%
                   \setlength\itemindent{-\leftmargin}%
                   \let\makelabel\descriptionlabel}}
   {\end{list}}

\newenvironment{listofsymbols}
   {\begin{list}{}{\setlength\labelwidth{0pt}%
                   \setlength\itemindent{-\leftmargin}%
                   \let\makelabel\descriptionlabel}}
   {\end{list}}


\begin{document}

Our network uses \gls{AD}. By using \gls{AD} with \gls{MS} bases clients that have been installed using a \gls{glos:RespF} from \gls{CD}, we can expect a high level of standardization.

\textbf{Some Greek symbols}: if you calculate with \gls{symb:Pi} you always get an irrational result, because \gls{symb:Pi} itself is irrational. As a matter of fact, there are \gls{symb:Phi} and \gls{symb:Lambda}, too.

\section*{\textsf{Glossary}}

\begin{glossary}
   \item[Active directory] Active Directory is the directory service for Windows based networks, that allows central organization and administration of any network resource. It allows a single-sign-on concept independent from network topologies or network protocols. As a prerequisite you need a Windows Server acting as Domain Controller. This computer stores all necessary data, e.\,g.~usernames and corresponding passwords.
   \item[Response file] A file that allows unattended software installation.
\end{glossary}

{\noindent}\rule{\linewidth}{2pt}

\section{Section}

Our network uses \citez{AD}. By using \citez{AD} with \citez{JS} bases clients that have been installed using a \citez{RF} from \citez{CD}, we can expect a high level of standardization.

\textbf{Some Greek symbols}: if you calculate with \citez{sym:pi} you always get an irrational result, because \citez{sym:pi} itself is irrational. As a matter of fact, there are \citez{sym:phi} and \citez{sym:lambda}, too.

\bibliographystyle{bibulous-glossaries}
\bibliography{gloss}


\end{document}